---
title: "Advanced Bioinformatics 2020 Assessment"
author: '9511'
date: "5/2/2020"
output:
  html_document
---

```{r}
library("ggplot2")
```
# Task 3.1
##  Use sum function and specify a vector of 5:55, and it will add all numbers between 5 and 55 together
```{r}
sum (5:55)
```
# Task 3.2
##  Assign a value of 10 to n and then create and run function sumfun
```{r}
n = 10
sumfun = sum(5:n)
sumfun
```
## Assign a value of 20 to n and then create and run function sumfun
```{r}
n = 20
sumfun = sum(5:n)
sumfun
```
##  Assign a value of 100 to n and then create and run function sumfun
```{r}
n = 100
sumfun = sum(5:n)
sumfun
```
# Task 3.3
## Set values as numeric for 12 entires of fibonacci
## Assign values for first 2 entries of fibonacci i.e. 1 and 1 
## Create loop for entries up to 12
```{r}
fibonacci = numeric(12)
fibonacci[1] = 1
fibonacci[2] = 1
for (i in 3:12) {fibonacci[i] = fibonacci[i-1] + fibonacci[i-2]}
fibonacci
```
# Task 3.4
```{r}
ggplot(data=mtcars,aes(x=as.factor(gear),y=mpg)) + geom_boxplot(aes(col=as.factor(gear)))
knitr::include_graphics
```

# Task 3.5
## Fit linear relationship using lm
```{r}
linearmodel <- lm(formula = dist ~ speed, data = cars)
linearmodel
```
## Intercept = -17.579, slope = 3.932
## Use summary function to get standard errors for intercept and slope
```{r}
summary(linearmodel)
```
## Intercept standard error = 6.7584, slope standard error = 0.4155
## Use ? function to get units used for variable in the cars dataset
```{r}
?cars
```
## Speed units = mph, Dist units = feet
# Task 3.6
```{r}
ggplot(cars,aes(speed,dist)) + geom_point() + geom_smooth(method="lm",formula="y~x")
knitr::include_graphics
```

# Task 3.7
## Convert units for dist from feet to meters
## Convert units for speed from mph to m/s and square
## Reaction time in seconds = distance/speed
## Assign values for x and y and model to get intecept and slope
```{r}
cars$dist <- cars$dist * 0.3048
cars$speed <- cars$speed * 0.44704
cars$speed <- cars$speed ^2
cars$reactiontime <- cars$dist / cars$speed
x <- cars$dist / cars$speed
y <- cars$reactiontime
linearmodel1 <- lm(formula = x ~ y, data = cars)
linearmodel1
```
## Use intercept and slope values in formula Y = β0 + β1X, sum all values and then divide by number of values in dataset to get average reaction time in seconds
```{r}
averagereactiontime = sum(3.14e-16 + (1.00e+00 * cars$reactiontime))/50
averagereactiontime
```
```{r}
ggplot(cars,aes(x,y)) + geom_point() + geom_smooth(method="lm",formula="y~x") + labs(y= "reaction time", x = "dist/speed^2")
knitr::include_graphics
```


